Assessing Bridge Condition in New York State Using Multiple Linear Regression

### 2024-12-04 paper/paper.qmd
Final prose update

## Overview
The objective of this methodology is to design a thorough system for collecting and analyzing traffic flow data across New York State bridges. This additional data addresses an essential limitation in the current dataset, which does not include traffic intensity—a key factor influencing bridge deterioration. By integrating traffic flow data, the enhanced model aims to improve its explanatory power and provide actionable recommendations for bridge maintenance prioritization. Rigorous sampling strategies and sophisticated data collection techniques are employed to ensure that the data is both representative and reliable, supporting more detailed policy and engineering decisions.

@@

By incorporating these dimensions, the target population captures the variability in bridge conditions and usage, enabling a detailed analysis of how traffic impacts structural integrity.

>>>>

## Overview
The objective of this methodology is to design a system for collecting and analyzing traffic flow data across New York State bridges. This additional data addresses an essential limitation in the current dataset, which does not include traffic intensity—a key factor influencing bridge deterioration. By integrating traffic flow data, the enhanced model aims to improve its explanatory power and provide actionable recommendations for bridge maintenance prioritization. Rigorous sampling strategies and sophisticated data collection techniques are employed to ensure that the data is both representative and reliable, supporting more detailed policy and engineering decisions.

@@

By incorporating these dimensions, the target population captures the variability in bridge conditions and usage, enabling an analysis of how traffic impacts structural integrity.
